### 2022-06-16 sections/3-methods.tex
PQ discussion

@@

Take the $k^{th}$ candidate.
Any cluster with $\delta^2 \leq \delta^2_k$ could contain one of the $k$-nearest neighbors of $q$.
Keep all such clusters in $candidates$ and exclude all other clusters.
Expand search to the children of all $candidates$ so far and repeat until all $candidates$ are leaf clusters.

>>>>

Add each cluster to a priority queue $m$ times, where $m$ is the cardinality of the cluster, and the priority is the $\delta^1$ distance of that cluster. 
Then, any cluster whose $\delta^2$ is greater than the $k^{th}$ highest $\delta^1$.

@@

Take the $k^{th}$ candidate.
Any cluster with $\delta^2 \leq \delta^1_k$ could contain one of the $k$-nearest neighbors of $q$.
Keep all such clusters in $candidates$ and exclude all other clusters.
Expand search to the children of all $candidates$ so far and repeat until all $candidates$ are leaf clusters.
